\begin{thanks}

Inscrutable mysteries underlying the horizon of our journey. Are often shady the paths that we must go. Many of our experiences stained our memories of greyish colors with ink that can not be changed. Still, certain tones, certain sounds, remain rooted in the foundations of memory working as anchors that prevent completely and eternally sink us. Some faces, some voices, some smiles, some advice, or an occasional correction are always pleasant company in our memories and encouragement when it comes to achieving the goals, to undertake new challenges and face major changes.

Thank God, eternal force that has design and order to this universe, so wonderful and mysterious, which again and again provides us with concerns and mysteries able to capture, inundate and complement the restless mind with which we have been provided.

%Thank you, your voice, your support and understanding, your joy and above all for your company.

%Thanks to my exfiancee, Carolina, for their endless support and patience, having been close to me in this way. By converting their desires and my desires in our dreams and goals. By having their life and purposes jointly with mine, forever hear my stories nonsense on relativity, quantum, philosophy and much more, always paying a tender and sincere interest. 
Thanks to my grandmother and aunt for hosting us and support us when the rest of the universe looked in another direction, thank you very much.

I strongly thank my advisor, Dr Jorge Silva, who has allowed me to be part of a multidisciplinary working group and integrate me in the development and formulation of innovative and relevant concepts. Thank you very much for allowing me to develop my thesis in areas of great importance to me. Thank you for your invaluable support and for the various tasks entrusted.

Thank you very much to my lab partners with whom I have developed and improved the results presented in this thesis. I wish to especially thank Hern\'an Calder\'on and his infinite knowledge of Latex without which there would have been possible to write this report.

Finally, to you, that for one reason or another uses this thesis, thank you very much and ¡Hasta Siempre!.

\begin{flushright}
Felipe Andr\'es Santib\'añez Leal.
\end{flushright}

\end{thanks}